\section{Symbolic Dynamic Programming}
\label{sec:sdp}

Symbolic dynamic programming (SDP) \cite{Boutilier_IJCAI_2001} is 
the process of performing dynamic programming via symbolic 
manipulation. In the following sections we present a brief overview
of SDP for zero-sum continuous stochastic games. We refer the reader
to \cite{Sanner_UAI_2011,Zamani_AAAI_2012} for more thorough 
expositions of SDP and its operations.

\subsection{Case Representation}

Symbolic dynamic programming assumes that all symbolic 
functions can be represented in case statement form \cite{Boutilier_IJCAI_2001} as follows:

{\small 
\abovedisplayshortskip=-5pt
\belowdisplayshortskip=0pt
\begin{equation*}
  f = 
    \begin{cases}
      \phi_1: & f_1 \\ 
      \vdots & \vdots\\ 
      \phi_k: & f_k \\ 
    \end{cases} \nonumber
\end{equation*}
}%

Here the $\phi_i$ are logical formulae defined over the state $\vec{x}$ 
and can include arbitrary logical combinations of boolean variables and 
linear inequalities over continuous variables. Each $\phi_i$ is
disjoint from the other $\phi_j$ ($j \neq i$) and may not 
exhaustively cover the state space. Hence, \emph{f} may only be a 
partial function. In this paper we restrict the $f_i$ to be either linear or constant 
functions of the state variable $\vec{x}$. We require $f$ to be continuous.

\subsection{Case Operations}

Unary operations on a case statement \emph{f}, such as scalar 
multiplication $c \cdot f$ where $ c \in \mathbb{R} $ or negation $-f$,
are applied to each $f_i$ ($1 \leq i \leq k$). 

Binary operations on two case statements are executed in two stages.
Firstly, the cross-product of the logical partitions of each case statement 
is taken, producing paired partitions. Finally, the binary operation 
is applied to the resulting paired partitions. The ``cross-sum'' $\oplus$
operation can be performed on two cases in the following manner:

{\small 
\abovedisplayskip=0pt
\belowdisplayskip=0pt
\begin{center}
  \begin{tabular}{r c c c l}
  &
    $\begin{cases}
        \phi_1: \hspace{-1mm} & \hspace{-1mm} f_1  \\ 
        \phi_2: \hspace{-1mm} & \hspace{-1mm} f_2  \\ 
    \end{cases}$
  $\oplus$
  &
  \hspace{-4mm}
    $\begin{cases}
        \psi_1: \hspace{-1mm} & \hspace{-1mm} g_1  \\ 
        \psi_2: \hspace{-1mm} & \hspace{-1mm} g_2  \\ 
    \end{cases}$
  &
  \hspace{-4mm} 
  $ = $
  &
  \hspace{-4mm}
    $\begin{cases}
      \phi_1 \wedge \psi_1: & f_1 + g_1 \\
      \phi_1 \wedge \psi_2: & f_1 + g_2 \\
      \phi_2 \wedge \psi_1: & f_2 + g_1 \\
      \phi_2 \wedge \psi_2: & f_2 + g_2  \\
    \end{cases}$
  \end{tabular}
\end{center}
}%

``cross-subtraction''  $\ominus$ and ``cross-multiplication'' $\otimes$
are defined in a similar manner but with the addition operator replaced
by the subtraction and multiplication operators, respectively.
Some partitions resulting from case operators may be inconsistent and 
are thus removed. 

Minimisation over cases, known as $\casemin$, is defined as:
\vspace{-6.5mm}
{\small 
\abovedisplayskip=0pt
\belowdisplayskip=0pt
\begin{center}
  \begin{tabular}{r c c c l}
  &
  \hspace{-7mm} $\casemin \Bigg(
    \begin{cases}
        \phi_1: \hspace{-1mm} & \hspace{-1mm} f_1 \\ 
        \phi_2: \hspace{-1mm} & \hspace{-1mm} f_2 \\ 
    \end{cases}$
  $,$
  &
  \hspace{-4mm}
    $\begin{cases}
        \psi_1: \hspace{-1mm} & \hspace{-1mm} g_1 \\ 
        \psi_2: \hspace{-1mm} & \hspace{-1mm} g_2 \\ 
    \end{cases} \Bigg)$
  &
  \hspace{-4mm} 
  $ = $
  &
  \hspace{-4mm}
    $\begin{cases}
      \phi_1 \wedge \psi_1 \wedge f_1 < g_1    : & \hspace{-2mm} f_1 \\ 
      \phi_1 \wedge \psi_1 \wedge f_1 \geq g_1 : & \hspace{-2mm} g_1 \\ 
      \phi_1 \wedge \psi_2 \wedge f_1 < g_2    : & \hspace{-2mm} f_1 \\ 
      \phi_1 \wedge \psi_2 \wedge f_1 \geq g_2 : & \hspace{-2mm} g_2 \\ 
      \vdots & \vdots
    \end{cases}$
  \end{tabular}
\end{center}
}%

$\casemin$ preserves the linearity of the constraints and the constant 
or linear nature of the $f_i$ and $g_i$. If the $f_i$ or 
$g_i$ are quadratic then the expressions $f_i > g_i$ or 
$f_i \leq g_i$ will be at most univariate quadratic and any such 
constraint can be linearised into a combination of at most two linear 
inequalities by completing the square. 

The $\casemax$ operator, which calculates symbolic case maximisation,
is defined as:
\vspace{-6.5mm}
{\small 
\abovedisplayskip=0pt
\belowdisplayskip=0pt
\begin{center}
  \begin{tabular}{r c c c l}
  &
  \hspace{-7mm} $\casemax \Bigg(
    \begin{cases}
        \phi_1: \hspace{-1mm} & \hspace{-1mm} f_1 \\ 
        \phi_2: \hspace{-1mm} & \hspace{-1mm} f_2 \\ 
    \end{cases}$
  $,$
  &
  \hspace{-4mm}
    $\begin{cases}
        \psi_1: \hspace{-1mm} & \hspace{-1mm} g_1 \\ 
        \psi_2: \hspace{-1mm} & \hspace{-1mm} g_2 \\ 
    \end{cases} \Bigg)$
  &
  \hspace{-4mm} 
  $ = $
  &
  \hspace{-4mm}
    $\begin{cases}
      \phi_1 \wedge \psi_1 \wedge f_1 > g_1    : & \hspace{-2mm} f_1 \\ 
      \phi_1 \wedge \psi_1 \wedge f_1 \leq g_1 : & \hspace{-2mm} g_1 \\ 
      \phi_1 \wedge \psi_2 \wedge f_1 > g_2    : & \hspace{-2mm} f_1 \\ 
      \phi_1 \wedge \psi_2 \wedge f_1 \leq g_2 : & \hspace{-2mm} g_2 \\ 
      \vdots & \vdots
    \end{cases}$
  \end{tabular}
\end{center}
}%
$\casemax$ preserves the linearity of the constraints and the constant 
or linear nature of the $f_i$ and $g_i$. 

Other important SDP operations include substitution and continuous maximisation. 
The substitution operation simply takes a set $\theta$ of variables and their
substitutions, e.g. $\theta = \left\{ x'_1/(x_1 + x_2), x'_2/x^2_{1} \text{exp}(x_2) \right\}$,
where the LHS of the / represents the substitution variable and the 
RHS of the / represents the expression that should be substituted in its place.
We can apply the substitution $\theta$ to both non-case functions $f_i$
and case partitions $\phi_i$ as $f_i\theta$ and $\phi_i\theta$, respectively.
Substitution into case statements can therefore be written as:

\vspace{-1.5mm}
{\small 
\abovedisplayshortskip=0pt
\belowdisplayshortskip=0pt
\begin{equation*}
  f\theta = 
    \begin{cases}
      \phi_1\theta: & f_1\theta \\ 
      \vdots & \vdots\\ 
      \phi_k\theta: & f_k\theta \\ 
    \end{cases} \nonumber
\end{equation*}
}%

Maximisation can be used to calculate $f_1(\vec{x}, y) = \contmax_{y}f_2(\vec{x}, y) $
with respect to a continuous parameter $y$. This is a complex case operation
whose explanation is beyond the scope of this paper. We refer the reader to 
\cite{Zamani_AAAI_2012} for further elucidation on this operator.

Case statements and their operations are implemented using Extended 
Algebraic Decision Diagrams (XADDs) \cite{Sanner_UAI_2011}.
XADDs provide a compact data structure with which to maintain
compact forms of $Q^{h}(\vec{x}, a_1, a_2)$ and $V^{h}(\vec{x})$. 
XADDs also permit the use of linear constraint feasibility checkers to 
prune unreachable paths in the XADD.

\subsection{SDP for Zero-sum Continuous Stochastic Games}

{\bf A class of zero-sum continuous stochastic games with a closed-form solution:} is specified
by piecewise constant rewards and a piecewise linear transition functions. In this 
section we show that SDP can be used to calculate optimal closed-form
solutions to this class of stochastic games.

We calculate the optimal solution to zero-sum CSGs by first
expressing $R(\vec{x}, a_1, a_2)$, $T(\vec{x}, a_1, a_2, \vec{x}')$, 
$V^0(\vec{x})$ as case statements. We also express $m_{a_{1}}$
as a trivial case statement representing an uninstantiated symbolic variable:

{\small 
\abovedisplayshortskip=-5pt
\belowdisplayshortskip=0pt
\begin{equation*}
  m_{a_{1}} = 
    \begin{cases}
      \top: & m_{a_{1}} \\ 
    \end{cases} \nonumber
\end{equation*}
}%

We can then compute the optimal solution via the following SDP equations:

{\footnotesize 
\abovedisplayskip=0pt
\belowdisplayskip=0pt
\begin{multline}
\label{eq:sdpdiscqfunc}
  Q^{h}(\vec{x}, a_1, a_2) = R(\vec{x}, a_1, a_2) \quad \oplus \\
  \gamma \otimes \int T(\vec{x}, a_1, a_2, \vec{x}') \otimes V^{h-1}(\vec{x}')\ d\vec{x}' 
\end{multline}
}%

{\footnotesize 
\abovedisplayskip=0pt
\belowdisplayskip=0pt
\begin{multline}
\label{eq:sdpdiscqfunc2}
  \tilde{Q}^{h}(\vec{x}, a_1, a_2) = \sum_{a_1 \in A_1} Q^{h}(\vec{x}, a_1, a_2) \otimes m_{a_{1}}
\end{multline}
}%

{\footnotesize 
\abovedisplayskip=0pt
\belowdisplayskip=0pt
\begin{multline}
\label{eq:sdpvfunccompact}
  V^{h}(\vec{x}) = \max_{m_{a_1}} \\ \left[ \left\{ \casemin \left( \tilde{Q}^{h}(\vec{x}, a_1, a_2),  \hat{Q}^{h}(\vec{x}, a_1, a_2) \right)  \forall a_2 \in A_2 \right\} \otimes \mathbb{I} \right]
\end{multline}
}%

Equations \eqref{eq:sdpdiscqfunc} and \eqref{eq:sdpvfunccompact} can
be derived from Equations \eqref{eq:csgdiscqfunc} and \eqref{eq:csgvfunccompact}
by replacing all functions and operations by their equivalent case
statements and case operations. For the sake of clarity we present
an intermediate step, Equation \eqref{eq:sdpdiscqfunc2}, in the calculation
of $V^{h}(\vec{x})$. In Equation \eqref{eq:sdpdiscqfunc2} 
$\tilde{Q}^{h}(\vec{x}, a_1, a_2)$ represents a $Q$ function that is 
weighted by the variable $m_{a_{1}}$. In Equation \eqref{eq:sdpvfunccompact} the first argument to the $\casemin$
operation is the previously calculated $\tilde{Q}^{h}(\vec{x}, a_1, a_2)$ and
the second argument is $\hat{Q}^{h}(\vec{x}, a_1, a_2)$, which is simply
$\tilde{Q}^{h}(\vec{x}, a_1, a_2)$ instantiated with a particular $a_2 \in A_2$.
Equation \eqref{eq:sdpvfunccompact} 
also includes an ``indicator'' function, $\mathbb{I}$, which serves as the summation constraint 
$\sum_{a_{1} \in A_1} m_{a_{1}} = 1$. The function $\mathbb{I}$
returns 1 when the conjunction of all constraints on each $m_{a_1}$ are satisfied
and $-\infty$, otherwise. That is:

\vspace{-2.5mm}
{\small 
\abovedisplayskip=0pt
\belowdisplayskip=0pt
\begin{multline*}
  \mathbb{I} = \\
  {\footnotesize
    \begin{cases}
      \forall a_{1} \in A_1 \hspace{6pt}\left[(m_{a_{1}} \geq 0) \wedge (m_{a_{1}} \leq 1 ) \wedge (\sum m_{a_{1}} = 1) \right]: 1 \\ 
      \forall a_{1} \in A_1 \neg \left[(m_{a_{1}} \geq 0) \wedge (m_{a_{1}} \leq 1 ) \wedge (\sum m_{a_{1}} = 1) \right]: -\infty \\ 
    \end{cases} \nonumber
   }
\end{multline*}
}%

The summation constraint is included to ensure that the subsequent
$\contmax$ operation returns legal values for $m_{a_1}$, since
$\contmax(l, -\infty) = l$.

In Algorithm 1 we present a methodology to calculate the optimal 
$h$-stage-to-go value function, $V^h(\vec{x})$, via Equations \eqref{eq:sdpdiscqfunc} -
\eqref{eq:sdpvfunccompact}. In the algorithm we notationally specify 
the arguments of the $Q^h$ and $V^h$ functions when they are 
instantiated by an operation. For the base case of $h = 0$, we set $V^0(\vec{x})$, expressed in 
case statement form, to zero or to the terminal reward. For all $h > 0$
we apply the previously defined SDP operations in the following steps:
\begin{enumerate}
  \item Prime the Value Function. 
            In line \ref{alg:prime} we set up a 
            substitution $\theta = \left\{ x_1/x'_1, \ldots, x_m/x'_m \right\}$, 
            and obtain $V'^{h} = V^{h}\theta$, the ``next state''.
  \item Discount and add Rewards. 
            We assume that the reward function
          contains primed variables and incorporate it in line \ref{alg:dr1}.
  \item Continuous Regression. For the continuous state variables in $\vec{x}$
            lines \ref{alg:cmi1} - \ref{alg:cmi2} follow the rules of integration w.r.t. a $\delta$ function 
            \cite{Sanner_UAI_2011} which yields the following symbolic
            substitution: 
            $\int f(x'_j) \otimes \delta\left[ x'_j - g(\vec{z})\right] dx'_j = f(x'_j)\left\{ x'_j/g(\vec{z})\right\}$,
            where $g(\vec{z})$ is a case statement and $\vec{z}$ does not contain $x'_j$.
            The latter operation indicates that any occurrence of $x'_j$ in $f(x'_j)$ is symbolically substituted
            with the case statement $g(\vec{z})$.
  \item Incorporate Agent 1's strategy. 
            At this point we have calculated $Q^h(\vec{x}, a_1, a_2)$, as shown in
            Equation \eqref{eq:sdpdiscqfunc}. In lines \ref{alg:dm1} - \ref{alg:dm2} 
            we weight the strategy for a specific $a_1$ by $m_{a_{1}}$.
            We note that $m_{a_{1}}$ is a case statement representing
            an uninstantiated symbolic variable.
  \item Case Minimisation. 
            In lines \ref{alg:cm1} - \ref{alg:cm2} we compute the best case for 
            $a_2$ as a function of all other variables. 
  \item Incorporate Constraints. 
            In line \ref{alg:constraint} we incorporate constraints on the $m_{a_{1}}$ variable: 
            $\sum_{a_{1} \in A_1} m_{a_{1}} = 1$ and 
            $m_{a_{1}} \geq 0 \wedge m_{a_{1}} \leq 1 \hspace{10pt} \forall a_{1} \in A_1 $.
            The $\casemin$ operator ensures that all case partitions which 
            involve illegal values of $m_{a_{1}}$ are mapped to $-\infty$.
  \item Maximisation. 
            In lines \ref{alg:max1} - \ref{alg:max2} we compute the best response
            strategy for every state. We note that this can only be done
            via symbolic methods since there are infinitely many states. At 
            this point we have calculated $V^{h}(\vec{x})$ as shown in 
            Equation \eqref{eq:sdpvfunccompact}.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Algorithm: CSG-VI
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\incmargin{1.5em}
\linesnumbered
\begin{algorithm}[ht!]
  \vspace{-.5mm}
  \dontprintsemicolon
  \SetKwFunction{remapWithPrimes}{Prime}
  
  \Begin{
  
    $V^0:=0, h:=0$\;
%    \;
    \While{$h < H$}{
      $h := h + 1$\;
      \emph{// Prime the value function}\;
      $Q^h := \remapWithPrimes{$V^{h-1}$} \,$ \; \label{alg:prime}
      %\;
      \emph{// Discount and add Rewards }\;
        $Q^h := R(\vec{x}, a_1, a_2, \vec{x}') \oplus (\gamma \otimes Q^h)$ \; \label{alg:dr1} 
      
      \emph{// Continuous Regression}\;
      \For {all $x'_j \in Q^h$}{ \label{alg:cmi1}
        $Q^h := \int Q^h \otimes T(x_j'|a_1, a_2, \vec{x}) \hspace{3pt} d_{x'_j}$\; \label{alg:cmi2}
      }
      %\;
%      \If{R does not contain primed variables} {
 %     $Q^h := R(\vec{x}, a_1, a_2) \oplus (\gamma \otimes Q^h)$ \; \label{alg:dr2}     
  %    }
  %    \;
      \emph{// Incorporate Agent 1's strategy }\;
      \For {all $a_1 \in A_1$}{ \label{alg:dm1}
        $Q^h := Q^h \oplus \left( Q^h\left(a_1\right) \otimes \{ \top : m_{a_{1}} \right) $ \; \label{alg:dm2}
      }
      %\;
      \emph{// Case Minimisation}\;
%      $Q^h := \casemin_{a_2} Q^{h} $\; \label{alg:cm}
      \For {all $a_2 \in A_2$}{ \label{alg:cm1}
        $Q^h := \casemin(Q^h, Q^h\left(a_2\right)) $ \; \label{alg:cm2}
      }
      %\;
      \emph{// Incorporate constraints }\;
      $Q^h := \casemin(Q^{h}, \mathbb{I}) $\; \label{alg:constraint}
      %\;
      \emph{// Maximisation}\;
      $V^h = Q^h$\;
      \For {all $a_1 \in A_1$}{ \label{alg:max1}
      $V^h := \contmax_{m_{a_{1}}} V^h\left(m_{a_{1}} \right)$ \; \label{alg:max2}
      }
      %\;
       \emph{// Terminate if early convergence}\;
      \If{$V^h = V^{h-1}$} {
        break 
        $\,$
      }
    }    
    \Return{$(V^h)$} \;
  }
  \caption{
    \footnotesize \texttt{CSG-VI}(CSG, $H$, $\mathbb{I}$) $\longrightarrow$ $(V^h)$ 
    \label{alg:csgvi}
  }
  \vspace{-1mm}
\end{algorithm}
\decmargin{.5em}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Algorithm: CSG-VI
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It can be proved that all of the SDP operations used in Algorithm 1 are
closed form for linear piecewise constant or linear piecewise linear
functions \cite{Sanner_UAI_2011,Zamani_AAAI_2012}. Given a linear 
piecewise constant $V^0(\vec{x})$ and closed form SDP operations, 
the resulting $V^{h+1}(\vec{x})$ will also be linear piecewise constant.
Therefore, by induction $V^{h+1}(\vec{x})$ is linear piecewise constant
for all horizons $h$.

%It can be proved that all SDP operations on case statements result in
%a linear piecewise constant $V^h(\vec{x})$, given a linear piecewise constant
%$V^0(\vec{x})$ \cite{Sanner_UAI_2011,Zamani_AAAI_2012}.

In the next section we demonstrate how SDP can be used to compute
exact solutions to a variety of zero-sum continuous stochastic games.