\section{Introduction}
%-----------------------------------------------------------------------------
%  What is the problem
%  Why is it interesting
%  What are your contributions
%  What is the outline
%-----------------------------------------------------------------------------

Modelling sequential competitive interactions between agents \\has 
important applications within economics and decision making. 
Stochastic games \cite{Shapley_PotNAoS_1953} provide framework 
a to model sequential interactions between multiple
non-cooperative \\agents. Zero-sum stochastic games stipulate that the
participating agents have diametrically opposing goals. 
Littman \cite{Littman_ICML_1994} presented a multiagent reinforcement
learning solution to discrete state zero-sum stochastic games. 
Closed form solutions for the continuous state case, however, 
remain unknown. Continuous state zero-sum stochastic games provide
a convenient framework with which to model many important financial
and economic domains, such as option valuation on derivative markets.

In this paper we present a novel technique to calculate a closed-form
solution to a subclass of continuous state zero-sum stochastic games. 
We show that by using symbolic dynamic programming we can calculate
closed-form solutions for arbitrary horizons.

We begin by presenting Markov Decision Processes (MDPs) and value
iteration \cite{Bellman_1957}, a commonly used dynamic programming
solution. We then describe both discrete and continuous stochastic 
games, game theoretic generalisations of the MDP framework. 
Following this we show how Symbolic Dynamic Programming (SDP) 
\cite{Boutilier_IJCAI_2001} can be used to calculate exact solutions
to a particular subclass of continuous zero-sum stochastic games. 
Finally, we present an empirical evaluation of our novel technique on 
an American option quitting game.