\section{Markov Decision Processes}
\label{sec:mdp}

A Markov Decision Process (MDP) \cite{Howard_1960} is defined by the tuple
$ \left\langle S, A, T, R, h, \gamma \right\rangle$. $S$ and $A$ 
specify a finite set of states and actions, respectively.
$T$ is a transition function $T : S \times A \rightarrow S$ which 
defines the effect of an action on the state. $R$ is the
reward function $R : S \times A \rightarrow \mathbb{R}$ which 
encodes the preferences of the agent. The horizon $h$ represents the 
number of decision steps until termination and the discount factor $\gamma$ 
is used to discount future rewards. In general, an agent's objective is 
to find a policy, $\pi : S \rightarrow A$, which maximises the expected 
sum of discounted rewards over horizon $h$.

Value iteration \cite{Bellman_1957} is a general dynamic programming 
algorithm used solve MDPs. For each horizon $h$, two functions form 
the basis of the algorithm: $V^{h}(s)$, the value of state $s$, and 
$Q^{h}(s, a)$, the value of taking action $a$ in state $s$. The two 
functions satisfy the following recursive relationship:
\begin{align}
  Q^{h}(s, a) &= R(s, a) + \gamma \sum_{s' \in S} T(s, a, s') V^{h-1}(s') \\
  V^{h}(s) &= \max_{a \in A} Q^{h}(s, a).
\end{align}

The algorithm is executed by first initialising $V^{0}$  to $R(s, a)$. 
Then for each $h$, the value function for $V^{h}(s)$ is calculated from $V^{h-1}(s)$
until the intended $h$-stage-to-go value function is computed.
Value iteration converges linearly in the number of iterations to the true
values of $Q(s, a)$ and $V(s)$ \cite{Bertsekas_1987}.

MDPs can be used to model multiagent systems under the assumption 
that other agents are part of the environment and have fixed behaviour. 
As a result, they ignore the difference between responsive agents and 
a passive environment \cite{Hu_ICML_1998}. In the next section we 
present a game theoretic framework which generalises MDPs to 
situations with two or more agents.