\section{Symbolic Dynamic Programming}
\label{sec:sdp}

Symbolic dynamic programming (SDP) \cite{Boutilier_IJCAI_2001} is 
the process of performing dynamic programming via symbolic 
manipulation. In the following sections we present a brief overview
of SDP and the data structures used to perform operations.

\subsection{Case Representation}

Symbolic dynamic programming assumes that all continuous symbolic 
functions can be represented in case form \cite{Boutilier_IJCAI_2001}.

\begin{equation}
  f = 
    \begin{cases}
      \phi_1: & f_1 \\ 
      \vdots & \vdots\\ 
      \phi_k: & f_k \\ 
    \end{cases} \nonumber
\end{equation}

$\phi_i$ are logical formulae defined over the state $\vec{x}$ 
and can include arbitrary logical combinations of boolean variables and 
linear inequalities over continuous variables. Each $\phi_i$ will be 
disjoint from the other $\phi_j$ ($j \neq i$) and may not 
exhaustively cover the state space. Hence, \emph{f} may only be a 
partial function. The $f_i$ may be either linear or quadratic 
in the continuous parameters. Operations on $f_i$ preserve the 
continuous nature of the function $f$.
 
%Symbolic dynamic programming assumes that all symbolic functions 
%can be represented in case form \cite{Boutilier_IJCAI_2001}, that is,
%
%\begin{equation}
  %f = 
    %\begin{cases}
      %\phi_1: & f_1 \\ 
      %\vdots & \vdots\\ 
      %\phi_k: & f_k \\ 
    %\end{cases} \nonumber
%\end{equation}
%
%where $\phi_i$ are logical formulae defined over the state $\vec{x}$ 
%that can include arbitrary logical ($\land, \lor, \neg$) combinations of 
%boolean variables and linear inequalities ($\geq, >, \leq, <$) over 
%continuous variables. The function \emph{f} is required to be continuous.
%
%Each $\phi_i$ will be disjoint from the other $\phi_j$ ($j \neq i$); 
%however the $\phi_i$ may not exhaustively cover the state space, hence
%\emph{f} may only be a partial function and may be undefined for 
%some variable assignments. The $f_i$ may be either linear or quadratic 
%in the continuous parameters according to the same restrictions as for 
%$R(\vec{x}, a, \vec{y})$.

\subsection{Case Operations}

Unary operations on a case statement \emph{f}, such as scalar 
multiplication $c \cdot f$ where $ c \in \mathbb{R} $ or negation $-f$,
are applied to each $f_i$ ($1 \leq i \leq k$). 

Binary operations on two case statements are executed in two stages.
Firstly, the cross-product of the logical partitions of each case statement 
is taken, producing paired partitions. Finally, the binary operation 
is applied to the resulting paired partitions. The ``cross-sum'' $\oplus$
operation can be performed on two cases in the following manner:

\begin{center}
  \begin{tabular}{r c c c l}
  &
    $\begin{cases}
        \phi_1: \hspace{-1mm} & \hspace{-1mm} f_1  \\ 
        \phi_2: \hspace{-1mm} & \hspace{-1mm} f_2  \\ 
    \end{cases}$
  $,$
  &
  \hspace{-4mm}
    $\begin{cases}
        \psi_1: \hspace{-1mm} & \hspace{-1mm} g_1  \\ 
        \psi_2: \hspace{-1mm} & \hspace{-1mm} g_2  \\ 
    \end{cases}$
  &
  \hspace{-4mm} 
  $ = $
  &
  \hspace{-4mm}
    $\begin{cases}
      \psi_1 \wedge \psi_1: & f_1 + g_1 \\
      \psi_1 \wedge \psi_2: & f_1 + g_2 \\
      \psi_2 \wedge \psi_1: & f_2 + g_1 \\
      \psi_2 \wedge \psi_2: & f_2 + g_2  \\
    \end{cases}$
  \end{tabular}
\end{center}

``cross-subtraction''  $\ominus$ and ``cross-multiplication'' $\otimes$
are defined in a similar manner but with the addition operator replaced
by the subtraction and multiplication operators, respectively.
Some partitions resulting from case operators may be inconsistent and 
are thus removed. 

Maximisation over cases, known as $\casemax$, is defined as:
\begin{center}
  \begin{tabular}{r c c c l}
  &
  \hspace{-7mm} $\casemax \Bigg(
    \begin{cases}
        \phi_1: \hspace{-1mm} & \hspace{-1mm} f_1 \\ 
        \phi_2: \hspace{-1mm} & \hspace{-1mm} f_2 \\ 
    \end{cases}$
  $,$
  &
  \hspace{-4mm}
    $\begin{cases}
        \psi_1: \hspace{-1mm} & \hspace{-1mm} g_1 \\ 
        \psi_2: \hspace{-1mm} & \hspace{-1mm} g_2 \\ 
    \end{cases} \Bigg)$
  &
  \hspace{-4mm} 
  $ = $
  &
  \hspace{-4mm}
    $\begin{cases}
      \phi_1 \wedge \psi_1 \wedge f_1 > g_1    : & \hspace{-2mm} f_1 \\ 
      \phi_1 \wedge \psi_1 \wedge f_1 \leq g_1 : & \hspace{-2mm} g_1 \\ 
      \phi_1 \wedge \psi_2 \wedge f_1 > g_2    : & \hspace{-2mm} f_1 \\ 
      \phi_1 \wedge \psi_2 \wedge f_1 \leq g_2 : & \hspace{-2mm} g_2 \\ 
      \vdots & \vdots
    \end{cases}$
  \end{tabular}
\end{center}

$\casemax$ preserves the linearity of its inputs. If the $f_i$ or 
$g_i$ are quadratic then the expressions $f_i > g_i$ or 
$f_i \leq g_i$ will be at most univariate quadratic and any such 
constraint can be linearised into a combination of at most two linear 
inequalities by completing the square.

\subsection{Extended Algebraic Decision Diagrams for Case Statements}

Case statements and their operations are implemented using Extended 
Algebraic Decision Diagrams (XADDs) \cite{Sanner_UAI_2011}.
XADDs provide a compact data structure with which to maintain
compact forms of $Q(\vec{x}, a_1, a_2)$ and $V(\vec{x})$. 
XADDs also permit the use of linear constraint feasibility checkers to 
prune unreachable paths in the XADD.

\subsection{SDP Solution Continuous Stochastic Games}

Symbolic dynamic programming can be used to find a closed-form
solution to a continuous stochastic game over an arbitrary horizon.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\incmargin{.5em}
\linesnumbered
\begin{algorithm}[H]
  \vspace{-.5mm}
  \dontprintsemicolon
  \SetKwFunction{regress}{Regress}
  
  \Begin{
    $V^0:=0, h:=0$\;
    \While{$h < H$}{
      $h:=h+1$\;
      
      $Q^h := \int V^{h-1} \otimes T(\vec{x}', \vec{x}, a_1, a_2) d_{\vec{x}'}$\;
      $Q^h := R(\vec{x}, a_1, a_2) \oplus (\gamma \otimes Q^h)$\;
      
      %$V^{h} := \casemax_{\pi_{a_1} \in \sigma(A_1)} \, Q_a^{h}$ $,$ \;      
      
      %\ForEach {$a(\vec{y}) \in A$}{
        %$Q_a^{h}(\vec{y})\,:=\,$\regress{$V^{h-1},a,\vec{y}$}\;
        %$Q_a^{h} := \casemin_{a_2 \in A_2} \, Q_a^{h}(\vec{y})$ $\,$\;
        %$V^{h} := \casemax_{\pi_{a_1} \in \sigma(A_1)} \, Q_a^{h}$ $,$ \;        
      %}
      
      \If{$V^h = V^{h-1}$} {
        break 
        $\,$ \emph{// Terminate if early convergence}\;
      }
    }    
    \Return{$(V^h)$} \;
  }
  \caption{
    \footnotesize \texttt{VI}(CSG, $H$) $\longrightarrow$ $(V^h)$ 
    \label{alg:vi}
  }
  \vspace{-1mm}
\end{algorithm}
\decmargin{.5em}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\incmargin{.5em}
\linesnumbered
\begin{algorithm}[H]
  \vspace{-.5mm}
  \dontprintsemicolon
  \SetKwFunction{remapWithPrimes}{Prime}
  %\SetKwFunction{sumout}{sumout}

  \Begin{
    $Q=$ \remapWithPrimes{$V$} $\,$ \emph{// All $ x_i \to x_i'$} \;
    \emph{// Continuous regression marginal integration}\\
    \For {all $x'_j$ in $Q$}{
      $Q := \int Q \otimes P(x_j'|\vec{x}, a_1, a_2) d_{x'_j}$\;
    }
    \Return{$R(\vec{x}, a_1, a_2) \oplus (\gamma \otimes Q)$} \;
  }
  \caption{
    \label{alg:regress}
    \footnotesize \texttt{Regress}($V, a_1, a_2$) $\longrightarrow$ $Q$   
  }
  \vspace{-1mm}
\end{algorithm}
\decmargin{.5em}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%