\section{Conclusions}
\label{sec:conclusion}

% Contributions
% Place work in wider context
% Future research directions

We have characterised a subclass of zero-sum continuous stochastic
games that can be solved exactly via parameterised linear optimisation.
We have also presented a novel symbolic dynamic programming 
algorithm that can be used to calculated exact solutions to this subclass
of stochastic games for arbitrary horizons. The algorithm
was used to calculate the first known exact solutions to a variety of 
experimental continuous domains.

%-----------------------------------------------------------------------------
%In this paper, we have introduced a novel symbolic dynamic programming
%technique to calculate exact solutions to a subclass of continuous state
%zero-sum stochastic games. Our key contributions are two-fold: we characterise
%a subclass of continuous stochastic games that can be solved 
%optimally in closed-form and we also prove that this solution remains
%closed-form for arbitrary horizons. This paper also represents the first
%extension of symbolic dynamic programming into game-theoretic domains.
%
%We believe that this work is the first to provide optimal closed-form
%solutions to continuous stochastic games with continuous state, 
%piecewise linear dynamics and piecewise constant reward. Furthermore,
%we assert that our experimental results are the first to provide
%exact solutions to their domains.

There are a number of avenues for future research. Firstly, it is important
to examine more general representations of the reward and transition functions while
still guaranteeing exact solutions. Another direction of research lies within
improving the scalability of the algorithm by using techniques such as 
bounded error compression for XADDs \cite{Vianna_UAI_2013} or lazy 
approximation of value functions as piecewise linear XADDs \cite{Li_AAAI_2005}. 
Search based approaches such as RTDP \cite{Barto_AI_1995} and HAO* \cite{Meuleau_JoAIR_2009}
are also readily adaptable to SDP. These extensions may then be used to 
model more complex financial and economic domains. Finally, SDP can be
used to calculate exact solutions to general sum games. The advances
made by this work open up a number of potential novel research paths
that we believe may help make progress in solving game theoretic domains
with continuous state.
