\section{Conclusions}
\label{sec:conclusion}

In this paper, we have introduced a novel symbolic dynamic programming
technique to calculate exact solutions to a subclass of continuous state
zero-sum stochastic games. Our key contributions are two-fold: we characterise
a subclass of continuous stochastic games that can be solved 
optimally in closed-form and we also prove that this solution remains
closed-form for arbitrary horizons. This paper also represents the first
extension of symbolic dynamic programming into game-theoretic domains.

We believe that this work is the first to provide optimal closed-form
solutions to continuous stochastic games with continuous state, 
piecewise linear dynamics and piecewise constant reward. Furthermore,
we assert that our experimental results are the first to provide
exact solutions to their domains.

There are a number of avenues for future research. Firstly, it is important
to examine generalisations of the reward and transition functions while
still guaranteeing exact solutions. Another avenue for research lies within
improving the scalability of the algorithm by using techniques such as 
bounded error compression for XADDs \cite{Vianna_UAI_2013}. Search based approaches
such as RTDP \cite{Barto_AI_1995} and HAO* \cite{Meuleau_JoAIR_2009}
are readily adaptable to SDP. These extensions may then be used to 
model more complex financial and economic domains. Finally, SDP can be
used to calculate exact solutions to general sum games.
