\section{Bayesian inference on graphical models with piecewise distributions}
\label{sec:inference_piecewise_models}
\paradot{Inference} We will present an inference method that can be generalized to  
a variety of graphical models with piecewise factors, however, our focus in this
work is on Bayesian networks factorized in the following
standard form 
\begin{equation}
\label{e:posterior}
pr(\boldsymbol\theta | \, d_1, \ldots, d_n) 
\propto
pr(\boldsymbol\theta, \, d_1, \ldots, d_n) 
= pr(\boldsymbol\theta) \cdot \prod_{i=1}^{n} pr(d_i | \boldsymbol\theta) , 
\end{equation} 
where $\boldsymbol\theta := (\theta_1, \ldots, \theta_N)$ is a parameter vector and $d_i$ are observed data points. 
A typical inference task %is the computation of the probability of a new data $d_{n+1}$ from the observed points:
with this posterior distribution is to compute the expectation of a function of $f(\boldsymbol\theta)$ given data:
\begin{equation}
\label{e:prob.outcome}
\mathbb{E}_{\boldsymbol\theta}[f(\boldsymbol\theta) \,|\, d_1, \ldots, d_n \,]
\end{equation}


\paradot{Piecewise models} 
We are interested in the inference on models where prior/likelihood distributions are piecewise.
A function $f(\boldsymbol{\theta})$ is $m$-piece \emph{piecewise} if it can be represented as:
\begin{equation}
\label{e:piecewise}
f(\boldsymbol{\theta}) = 
{\footnotesize
\begin{cases}
\phi_1(\boldsymbol{\theta}) : & f_1(\boldsymbol{\theta})\\
\vdots\\
\phi_m(\boldsymbol{\theta}) : & f_m(\boldsymbol{\theta})
\end{cases}
}%end footnote size
\end{equation}
where $\phi_1$ to $\phi_m$ are mutually exclusive and jointly exhaustive Boolean functions (constraints) 
that partition the space of variables $\boldsymbol{\theta}$. If for a particular variable assignment $\boldsymbol{\theta}_0$, a constraint $\phi_i(\boldsymbol{\theta}_0)$ is satisfied, then by definition, the function returns the value of its $i$-th \emph{sub-function}: $f(\boldsymbol{\theta}_0) = f_i(\boldsymbol{\theta}_0)$.  
In this case, it is said that sub-function $f_i$ is \emph{activated} by assignment $\boldsymbol{\theta}_0$.


In the implementation of our proposed algorithm, the constraints are restricted to linear/quadratic (in)equalities while sub-functions are polynomials with real exponents. % in which real-exponents 
%(except -1) -- no reason you cannot handle this
%are allowed.
However, in theory, the algorithm can be applied to \emph{any} family of piecewise models in which the roots of univariate constraint expressions can be found and sub-functions (and their products) are integrable. 

%In Example~\ref{example:pref}, BPPL is a \emph{piecewise constant} model in the sense that both prior and likelihood models are piecewise and their corresponding \emph{sub-functions} ($f_i$) are constant. A more general piecewise model where the sub-functions are not constant is presented in  Section~\ref{sect:experiment}. 

\paradot{Complexity of inference on piecewise models}
If in the model of equation \ref{e:posterior}, the prior $pr(\boldsymbol\theta)$ 
is an $L$-piece distribution and each of the $n$ likelihoods is a piecewise function with number of partitions  bound by $M$, 
then the joint distribution is a piecewise function with number of partitions bound by $LM^n$ (therefore, $O(M^n)$).
The reason, as clarified by the following simple formula,   
is that the number of partitions in the product of two piecewise functions is bound by the product of their number of partitions:\footnote{
If pruning potential inconsistent (infeasible) constraint is possible
(i.e.\ by \emph{linear constraint solvers} for linear constrains) and the imposed extra costs are justified,
the number of partitions can be less.
}%endfootnote

{\footnotesize
\begin{align}
&\begin{cases}
\phi_1(\boldsymbol{\theta}) : &\!\!\!\!\! f_1(\boldsymbol{\theta})\\
\phi_2(\boldsymbol{\theta}) : &\!\!\!\!\! f_2(\boldsymbol{\theta})
\end{cases}
\otimes
\begin{cases}
\psi_1(\boldsymbol{\theta}) : &\!\!\!\!\! g_1(\boldsymbol{\theta})\\
\psi_2(\boldsymbol{\theta}) : &\!\!\!\!\! g_2(\boldsymbol{\theta})
\end{cases}
\!\!\!=\!\!
\begin{cases}
\phi_1(\boldsymbol{\theta}) \wedge \psi_1(\boldsymbol{\theta}) :\!\!\!\!\! & f_1(\boldsymbol{\theta}) g_1(\boldsymbol{\theta})\\
\phi_1(\boldsymbol{\theta}) \wedge \psi_2(\boldsymbol{\theta}) :\!\!\!\!\! & f_1(\boldsymbol{\theta}) g_2(\boldsymbol{\theta})\\
\phi_2(\boldsymbol{\theta}) \wedge \psi_1(\boldsymbol{\theta}) :\!\!\!\!\! & f_2(\boldsymbol{\theta}) g_1(\boldsymbol{\theta})\\
\phi_2(\boldsymbol{\theta}) \wedge \psi_2(\boldsymbol{\theta}) :\!\!\!\!\! & f_2(\boldsymbol{\theta}) g_2(\boldsymbol{\theta})
\end{cases}
\end{align}
}%end footnote size
\noindent{\bf Exact inference on piecewise models.} In theory, closed-form inference on piecewise models (at least piecewise polynomials) with linear constraints is possible \cite{Sanner:12}.
In practice, however, such symbolic methods rapidly become intractable since the posterior requires
the representation of $O(M^n)$ distinct case partitions.
%For example, by rule of thumb, a few observed data points with simple piecewise likelihood models lead to
%joint/posterior distributions with tens of partitions.
%For an inference problem formalized by equation~\ref{e:prob.outcome}, 
%the number of required marginalization integrals is $|\boldsymbol\theta|$ (dimensionality of the parameter space).
%Although that the family of piecewise polynomials are closed under integration, even a single \emph{closed form} integral over such a posterior can lead to a function with thousands of pieces \cite{Sanner:12}.   
   
\paradot{Approximate inference on piecewise modes} 
An alternative option is to seek \emph{asymptotically unbiased} inference methods
via Monte Carlo sampling.
%The existing such tools are based on sampling.
Given a set of $S$ samples (particles) $\{\boldsymbol\theta^{(1)}, \ldots, \boldsymbol\theta^{(S)}\}$ taken from a posterior $pr(\boldsymbol\theta | \, d_1, \ldots, d_n)$, 
the inference task of Equation~\ref{e:prob.outcome} can be approximated by: 
$\frac{1}{S} \sum_{i=1}^S f(\theta^{(i)} | \, d_1, \ldots, d_n)$.
Three widely used sampling methods for an arbitrary distribution $pr(\boldsymbol\theta | \, d_1, \ldots, d_n)$ are the following:
% Three widely used methods to sample $S$ from an arbitrary $pr(\boldsymbol\theta | \, d_1, \ldots, d_n)$ are as follows:

\emph{Rejection sampling}:
Let $p(\boldsymbol{\theta})$ and $q(\boldsymbol{\theta})$ be two distributions 
such that direct sampling from them is respectively hard and easy
and
$p(\boldsymbol{\theta})/q(\boldsymbol{\theta})$ is bound by a constant $c>1$. 
To take a sample from $p$ using \emph{rejection sampling}, 
a sample $\boldsymbol{\theta}$ is taken from distribution $q$ and accepted with probability $p(\boldsymbol{\theta}) / c q(\boldsymbol{\theta})$, 
otherwise it is rejected and the process is repeated. 
If $c$ is too large, the speed of this algorithm is slow since often lots of samples are required until one is accepted.

\emph{Metropolis-Hastings (MH)}:
To generate a new Markov Chain Monte Carlo (MCMC) sample $\boldsymbol{\theta}^{(t)}$ of a distribution $p(\boldsymbol{\theta})$ given a previously taken sample $\boldsymbol{\theta}^{(t-1)}$, 
firstly, a sample $\boldsymbol{\theta}'$ is taken 
from a symmetric \emph{proposal density} $q(\boldsymbol{\theta} |\, \boldsymbol{\theta}^{(t-1)})$ 
%from which samples can be taken efficiently 
(often an isotropic \emph{Gaussian} centered at $\boldsymbol{\theta}^{(t-1)}$). 
With probability $\min \big(1, q(\boldsymbol{\theta}^{(t-1)}|\boldsymbol{\theta}')p(\boldsymbol{\theta}')/q(\boldsymbol{\theta}'|\boldsymbol{\theta}^{(t-1)})p(\boldsymbol{\theta}^{(t-1)}) \big)$, 
$\boldsymbol{\theta}'$ is accepted $\boldsymbol{\theta}^{(t)} \leftarrow \boldsymbol{\theta}'$, otherwise, $\boldsymbol{\theta}^{(t)} \leftarrow \boldsymbol{\theta}^{(t-1)}$. 
Choosing a good \emph{proposal} is problem-dependent and requires tuning. Also most of proposals that often require costly posterior evaluation is rejected leading to a poor performance. 


\emph{Gibbs sampling}:
A celebrated MCMC method in which generating new samples $\boldsymbol{\theta} = (\boldsymbol{\theta}_1, \ldots, \boldsymbol{\theta}_N)$ requires each variable $\boldsymbol\theta_i$ to be sampled conditioned on
% In this MCMC method, to generate a new sample for $\boldsymbol{\theta} = (x_1, \ldots, x_N)$, 
% each variable is sampled conditioned on 
the last instantiated value of the others:
$\boldsymbol{\theta}_i \sim p(\boldsymbol{\theta}_i | \boldsymbol{\theta}_{-i})$. 
%Therefore,  
Computation of $N$ univariate \emph{cumulative distribution functions} (CDFs) 
(one for each $p(\boldsymbol{\theta}_i | \, \boldsymbol{\theta}_{-i})$) as well as their inverse functions is required which can be quite time consuming. 
In practice, when these integrals are not tractable or easy to compute Gibbs sampling can be prohibitively expensive.   

Compared to rejection sampling or MH, the performance of Gibbs sampling on the aforementioned \emph{piecewise} models is exponential in the number of observations and attributes.  
In this work, we propose an alternative linear Gibbs sampler. % that is linear in the number of data points and attributes.
%However,  we are going to propose a novel Gibbs-based sampling method which is scalable in the amount of data.

%\paradot{Gibbs sampling from a piecewise model}
%CDF of a piecewise (univariate) function is clearly the summation of the CDFs of each of its partitions.
%is affected by does not get around the difficulties introduced by the exponential growth of posterior distributions in Bayesian models.\footnote{The reason is that the number of pieces in a function of form $p(x_i |\, \boldsymbol{\theta}_{-i})$ is still in $O(M^n)$. In practice, many univariate partitions might be empty (i.e.\ associated with infeasible constraints) but in general, detecting them is not such easier than computing CDFs.
%} %end footnote  
%Therefore, according to the previous arguments, using Gibbs to take a single sample vector from the posterior distribution of an $N$ dimensional space of a Bayesian inference model with an $L$-piece prior and $n$ $M$-piece likelihood functions, up to $LM^nN$ CDFs (and CDF$^{-1}$s) should be computed.
%With the aim of making Gibbs sampling more scalable, in Section~\ref{sect:mix} we introduce a technique using which this number can be reduced to {\color{red}an order of} $LM(N+n)$.

