\section{Conclusions}
\label{sec:conclusion}

% Contributions

In this paper we have characterised a subclass of zero-sum continuous stochastic
games that can be solved exactly via parameterised linear optimisation. 
We have also presented a novel symbolic dynamic programming 
algorithm that can be used to calculate exact solutions to this subclass
of games for arbitrary horizons. The algorithm was used to calculate the first known 
exact solutions to a variety of continuous stochastic games with piecewise constant reward
and piecewise linear transitions.

% Future Research Directions

There are a number of avenues for future research. Firstly, it is important
to examine more general representations of the reward and transition functions while
still guaranteeing exact solutions. Another direction of research lies within
improving the scalability of the algorithm by either extending techniques for Algebraic
Decision Diagrams \cite{Bahar_JoFMiSD_1993} from APRICODD \cite{St-Aubin_NIPS_2000} under 
the current restrictions on the reward and transition functions, bounded error compression for 
XADDs \cite{Vianna_UAI_2013} for more expressive representations, or lazy 
approximation of value functions as piecewise linear XADDs \cite{Li_AAAI_2005}. 
Search based approaches such as RTDP \cite{Barto_AI_1995} and HAO* \cite{Meuleau_JoAIR_2009}
are also readily adaptable to SDP. These extensions may then be used to model sequential decision making in 
more complex financial and economic domains. Finally, SDP can be
used to calculate exact solutions to general sum stochastic games. The advances
made within this paper open up a number of potential novel research paths
which may be used to progress solutions to sequential game theoretic domains
with continuous state.
